### 2020-11-21 Thesis-Chapter2-Background.tex
Fix LEAD->LAED act term

    \law{2020}{The \acf{LEADAct}}{\cite{graham_2020}}{

Introduced by the same senator as the \ac{EARNITAct}, the \ac{LEADAct} is a direct attack on encryption. The
\ac{LEADAct} specifically addresses \ac{DAR} and \ac{DIM} by forcing device, operating system, and application
developers to implement the ability to decrypt all data stored or passing through the device or software system
``concurrently with their transmission'' ``unless the independent actions of an unaffiliated entity make it technically
impossible to do so.'' The act neither mandates nor recommends any technical approach to providing this capability.

@@

As this relates to \ac{EA}, Fourth Amendment interpretation determines the threshold at which authorities require a
warrant, not what demands they can or cannot make once they have one (e.g. demands for access to \ac{plaintext}). As
mentioned above, the FBI argued in the San Bernardino case that the \ac{AWA} grants it authority to demand access,
though it is strongly argued that \acs{CALEA} explicitly precludes this kind of demand \cite{gidari_2016}. Since the FBI
dropped the case, the matter is not formally settled, though the consensus is that legislation such as the \ac{LEADAct}
is required before courts would uphold that command.

@@

Looking ahead, there are three types of cases through which the judicial branch could have a strong effect on digital
privacy policy. First, Fourth Amendment cases will establish classes of protected data and thresholds for warrants.
Second, a Supreme Court Fifth Amendment case could settle under what circumstances, if any, a password could be
compelled. Third, a surprise \ac{AWA} ruling could open the door to demands for access, though legislation like
\ac{LEADAct} is more likely to have this effect.

>>>>

    \law{2020}{The \acf{LAEDAct}}{\cite{graham_2020}}{

Introduced by the same senator as the \ac{EARNITAct}, the \ac{LAEDAct} is a direct attack on encryption. The
\ac{LAEDAct} specifically addresses \ac{DAR} and \ac{DIM} by forcing device, operating system, and application
developers to implement the ability to decrypt all data stored or passing through the device or software system
``concurrently with their transmission'' ``unless the independent actions of an unaffiliated entity make it technically
impossible to do so.'' The act neither mandates nor recommends any technical approach to providing this capability.

@@

As this relates to \ac{EA}, Fourth Amendment interpretation determines the threshold at which authorities require a
warrant, not what demands they can or cannot make once they have one (e.g. demands for access to \ac{plaintext}). As
mentioned above, the FBI argued in the San Bernardino case that the \ac{AWA} grants it authority to demand access,
though it is strongly argued that \acs{CALEA} explicitly precludes this kind of demand \cite{gidari_2016}. Since the FBI
dropped the case, the matter is not formally settled, though the consensus is that legislation such as the \ac{LAEDAct}
is required before courts would uphold that command.

@@

Looking ahead, there are three types of cases through which the judicial branch could have a strong effect on digital
privacy policy. First, Fourth Amendment cases will establish classes of protected data and thresholds for warrants.
Second, a Supreme Court Fifth Amendment case could settle under what circumstances, if any, a password could be
compelled. Third, a surprise \ac{AWA} ruling could open the door to demands for access, though legislation like
\ac{LAEDAct} is more likely to have this effect.
